### 2017-01-23 chapters/ch2-bottom-up.tex
Clarify setup phase, settings for Emacs

To prepare a chain on node $x$ for validation in consensus run $n$, $x$ first
communicates to the validators of consensus run $n-1$ for the valid set of
blocks (recall that we assume every node knows the validators), and then
generates a new checkpoint block (\cref{fig:protocol-setup}). This completes
the setup phase.

@@

>>>>

To prepare a chain on node $x$ for validation in consensus run $n$, $x$ first
communicates to the validators of consensus run $n-1$ for the Merkle hash of the
valid set of blocks (recall that we assume every node knows the validators), and
then generates a new checkpoint block (\cref{fig:protocol-setup}). This
completes the setup phase.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End:
